---
title: "Kickstarter Analysis - Level 1"
author: "Elena Dubova"
date: "7/1/2020"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE, echo=FALSE}
require("knitr")
opts_knit$set(root.dir = '/Users/elena/GitHub/Data-Stories/explore/r', include=FALSE)
```

## Importing data

```{r}

data <- read.csv("kickstarter.csv")

```

```{r}
head(data, 3)
```

### Visualization

Boxplot of goal, pledged and bakers.
```{r}
boxplot(data$goal)
```


```{r}
boxplot(data$usd.pledged)
```


```{r}
boxplot(data$backers)
```

Wow, outliers attack us! This is a pretty common scenario. Let's get rid of them!

```{r}
new <- data[data$backers < 150,]
new <- new[new$goal < 30000,]
new <- new[new$usd.pledged < 15000,]
```

```{r}
boxplot(new$goal)
```

```{r}
boxplot(new$usd.pledged)
```

```{r}
boxplot(new$backers)
```

Histogram of goal, pledged, and bakers.
```{r}
hist(new$usd.pledged)
```
```{r}
hist(new$goal)
```
```{r}
hist(new$backers)
```


What state is most common?

```{r}
temp = table(new$state)
barplot(temp, horiz = FALSE, main='Main Categories', axes=TRUE,beside = FALSE)

```

Finally, let's have a look at variable relations:

We are mostly interested in **success** and **failure**, so let's filter them out for clarity.

```{r}
new <- new %>%
  filter(state %in% c('failed', 'successful'))

```


```{r}
color_var <- as.factor(new$state)
plot(new$usd.pledged, new$backers, pch=1, col=color_var)
legend("topleft", legend=levels(color_var), pch=1, col=unique(color_var))
```

```{r}
color_var <- as.factor(new$state)
plot(new$goal, new$usd.pledged, pch=1, col=color_var)
legend("topleft", legend=levels(color_var), pch=1, col=unique(color_var))
```

Sometimes it is useful to log-transform the variables to see relations, but we should be careful with it - you are changing the meaning of the variable! 

```{r}

plot(log2(new$usd.pledged), log2(new$backers), col=as.factor(new$state))
```


```{r}
plot(log(new$goal), log(new$usd.pledged), col=as.factor(new$state))
```

We can try pair plot as well

```{r}
data %>%
  select(where(is.numeric)) %>%
  pairs()
```

What is your story about Kickstarter projects now? Feel free to explore more and share!