---
title: "Kickstarter Analysis - Level 2"
author: "Elena Dubova"
date: "7/1/2020"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE, echo=FALSE}
require("knitr")
opts_knit$set(root.dir = '/Users/elena/GitHub/Data-Stories/explore/r', include=FALSE)
```

## Importing data

```{r}

data <- read.csv("kickstarter.csv")

```

```{r}
head(data, 3)
```

## Exploratory Data Analysis

```{r}

library(dplyr)

```

### Looking into the numbers

Get mean and median values for goals.
```{r}

data %>%
  summarize(mean = mean(goal), median = median(goal))

```

Get minimum and maximum goals.
```{r}

data %>%
  summarize(minimum = min(goal), maximum = max(goal), range=max(goal)-min(goal))


```

Get variance and standard deviation.
```{r}

data %>%
  summarize(variance = var(goal), std_dev1 = sd(goal), std_dev2 = sqrt(variance))

```

Get quantiles
```{r}

data %>%
  summarize(q_25 = quantile(goal,0.25), 
            q_75 = quantile(goal,0.75), 
            iqr1 = q_75-q_25, 
            iqr2 = IQR(goal))

```

Get it all in one nice table 
```{r}

data %>%
  summarize(mean = mean(goal), 
            median = median(goal),
            minimum = min(goal), 
            maximum = max(goal), 
            range=max(goal)-min(goal),
            variance = var(goal), 
            std_dev = sd(goal),
            q_25 = quantile(goal,0.25), 
            q_75 = quantile(goal,0.75), 
            iqr = IQR(goal)
            )

```

Numbers are good. Now let us get sense of categories.

Count values in each main_category. What is the most and least popular category? What is the median goal within each category?
```{r}
data %>%
  group_by(main_category) %>%
  summarise(count = n(), mean_goal = mean(goal)) %>%
  arrange(desc(mean_goal))

```

You do not have to use dplyr to explore categories. Base package also has nice functions.
```{r}
table(data$main_category)
```

Let's see what makes a successful project. How different is the mean?

```{r}

data %>%
  filter(state %in% c('failed', 'successful')) %>%
  group_by(state) %>%
  summarize(count = n(), 
            mean_goal = mean(goal))

```

Let's see what makes a successful project (and consider its category this time).

```{r}
data %>%
  filter(state == 'successful') %>%
  group_by(main_category) %>%
  summarize(count = n(), 
            mean_goal = mean(goal)) %>%
  arrange(desc(count)) %>%
  top_n(10)

```
